Prefetching SPARQL query cacher

### 2016-05-31 dissertation/cache-proxy.tex
restrict to practicals and HTTP

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL Endpoint
or hypermedia metadata. In practice, there is very little
information. If the cache is to be shared, then it would typically
reside on the forward proxy, or in a CDN.

>>>>

My interest is the case where the caching proxy has no further
knowledge of the data than what is exposed through the SPARQL Endpoint
or hypermedia metadata. While this would be known as a mediator in the
database literature and has also been a field of study for 20 years, I
focus on a practical motivation stemming mainly from what is currently
available, and in practice, there is very little information. Also,
this study is also practically restricted to HTTP. If the cache is to
be shared, then it would typically reside on the forward proxy, or in
a CDN.
